\vspace{-2em}The 4th Workshop on Sustainable Software for Science: Best Practices and Experiences (WSSSPE4)

### 2016-06-11 WSSSPE4_proposal/WSSSPE4_proposal.tex
more work in assessment

The program committee currently has about 60 global members, from academia, industry, and national labs, with more invitations outstanding.  See the web site (\url{http://wssspe.researchcomputing.org.uk/wssspe4/}) for the specific names.

@@

Reports describing the activities of WSSSPE and WSSSPE2 culminated in peer-reviewed articles~\cite{WSSSPE1,WSSSPE2}, while the report from WSSSPE3 is currently undergoing peer review (and is available via arXiv)~\cite{WSSSPE3}; all reports are publicly available via publication in an open-access journal.
A similar report will be prepared at the conclusion of WSSSPE4, and following the practices of past workshops will be written collaboratively and openly on GitHub.

@@

We will assess the success of WSSSPE4 with two different mechanisms.
For Track 1, the activities and\slash or deliverables proposed during the workshop (and documented in the report) will be evaluated for progress or completion six months following the workshop.
This could include submission of proposals or papers, or the creation of other useful products (e.g., tutorials, wiki, forum).
Track 2 activities will be assessed by surveying attendees following the workshop with questions such as ``What software development practices are you aware of now that you were not aware of prior to WSSSPE4?'' and ``What practices do you intend on implementing in your own software development work following WSSSPE4?''.
In addition, the submission of a workshop report for peer review within six months will be another metric for success.

\textcolor{red}{How will we know if this is successful? - for track 2, survey attendees?  for track 1, see if we have proposals submitted or activities underway six months later?}
\textcolor{blue}{I tried fleshing those suggestions about a bit; what about assessment of efforts to get people from underrepresented groups involved?}

>>>>

The program committee currently has about 65 global members, from academia, industry, and national labs, with more invitations outstanding.  See the web site (\url{http://wssspe.researchcomputing.org.uk/wssspe4/}) for the specific names.

@@

Reports describing the activities of WSSSPE and WSSSPE2 culminated in peer-reviewed articles~\cite{WSSSPE1,WSSSPE2}, while the report from WSSSPE3 is currently undergoing peer review (and is available via arXiv)~\cite{WSSSPE3}; all reports are publicly available via publication in an open-access journal.
A similar report will be prepared at the conclusion of WSSSPE4, and following the practices of past workshops, will be written collaboratively and openly on GitHub.

@@

We will assess the success of WSSSPE4 with two different mechanisms.
For Track 1, the activities and\slash or deliverables proposed during the workshop (and documented in the report) will be evaluated for progress or completion six months following the workshop.
This could include submission of proposals or papers, or the creation of other useful products (e.g., tutorials, wiki, forum).
Track 2 activities will be assessed by surveying attendees following the workshop with questions such as ``What software development practices are you aware of now that you were not aware of prior to WSSSPE4?'' and ``What practices do you intend on implementing in your own software development work following WSSSPE4?''.
In addition, the peer review process for a report on the workshop, to be submitted within six months from the end of the conference, will be another metric for success.

In our final report, we will discuss the demographics of the supported attendees, the compete set of workshop attendees, speakers, breakout group leads, and the leaders of activities that grow out the workshop. In all cases, while our ideal would be to have these demographics match the US or global population averages, our goal will be to significantly improve over academic STEM and tech industry norms.
